Paper without a name

### 2014-05-30 Article.tex
Changes..
Changes.

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}

@@

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

@@

The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from
the top), we try to generate all the permutations of these wires by using boxes.
A box takes two wires, and is allowed to swap these wires. We can concatenate
these boxes to get a configuration of boxes.  The configuration is said valid
if, by swapping or not the wires on every box, we can obtain any permutation of
    the $n$ wires.

Mathematically, we consider that the wires are numbers from 1 to $n$. A box is a
permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ is equal to 0
or 1.  A configuration of boxes $C$ is the concatenation of $k$ boxes $\tau_1,
\ldots, \tau_k$, that means, $C(\epsilon_1, \ldots, \epsilon_k) =
\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration $C$ is
said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.

Given this problem, we tried to determine the best lower bound of the number of
boxes $k$.

We can easily determine trivial lower and upper bounds of the number of
boxes~:\\ Given the fact that $C$ is an application, we need to have
$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediateley obtain that $k$
has to be greater than $\log_2(n!)$.\\ We also have an upper bound~: The
traditionnal bubblesort is a valid configuration of the SwitchBoxes problem. We
obtain that the optimal $k$ is smaller than $\frac{(n-1)(n-2)}{2}$.

@@

\begin{verbatim}

    function FindPos(n, T, begin, end)   // find n in T(begin, begin+1, ..., end-1)
        assert(begin < end)
        if begin + 1 = end then
            return begin
        else
            mid = E[(begin + end) / 2]
            if T[mid] > n then
                return FindPos(n, T, begin, mid)
            else
                return FindPos(n, T, mid+1, end)

    function Sort(T)
        n = T.size
        S = [T[0]]
        for i = 1 to n-1
            pos = FindPos(T[i], S, 0, S.size)
            insert T[i] in S at position pos
        return S

\end{verbatim}

@@

@@

$n=2$ : $S_2(e_1) = (1,2)^{e_1}$

$n=3$ : $S_3(e_1,e_2,e_3) = (1,2)^{e_1} \circ (2,3)^{e_2} \circ (1,2)^{e_3}$

$n=4$ : $S_4(e_1,e_2,e_3,e_4,e_5) = (1, 2)^{e_1} \circ (3,4)^{e_2} \circ
(1,3)^{e_3} \circ (2, 4)^{e_4} \circ (1,2)^{e_5}$

@@

$$S_2 = (1,2)$$

$$S_3 = (1,2)(2,3)(1,2)$$

$$S_4 = (1,2)(3,4)(1,3)(2,4)(1,2)$$

@@

$$S_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$

@@

$$
\begin{aligned}
    S_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
        & = & (0,1)(2,3)(4,5)(6,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,4)(1,5)(2,6)(3,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,1)(2,3)(4,5)(6,7)
\end{aligned}$$

@@

For $n$ which is not a power of two, we construct $S_n^0$ by taking
$S_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.

For example, $S_5^0$ can be generated from $S_8^0$ and by removing quite a lot
of the boxes. We obtain the following solution :

$$S_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}

@@

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

The SwitchBoxes problem is a combinatory problem. Given $n$ wires, we try to
generate all the permutations of these wires by using boxes.  A box takes two
wires and a control bit, and swaps the two entry wires iff the control bit is
set. We can concatenate these boxes to get a configuration of boxes.  The
configuration is said valid if, by giving the set of boxes different
configurations (ie. swapping or not the wires on every box), we can obtain any
permutation of the $n$ wires.

Mathematically, we consider that the wires are numbers from 1 to $n$. A box is a
permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ represents the
control bit for the box and is either 0 or 1.  A configuration of boxes $C$ is
the concatenation of $k$ boxes $\tau_1, \ldots, \tau_k$, that means,
$C(\epsilon_1, \ldots, \epsilon_k) =
\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration $C$
is said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.

Given this problem, we tried to determine the best lower bound of the number of
boxes $k$ which is valid for $\mathfrak{S}_n$, ie generates all the permutations of $n$
wires.

We can easily determine trivial lower and upper bounds of the number of
boxes~:\\ Given the fact that $C$ is an application, we need to have
$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediately obtain that $k$
has to be greater than $\log_2(n!)$.\\ We also have an upper bound~: The
traditional bubblesort gives a valid configuration of the SwitchBoxes problem. We
obtain that the optimal $k$ is smaller than $\frac{(n-1)(n-2)}{2}$.

@@

\begin{algorithm}
\begin{algorithmic}
\Function{FindPos}{$n, T, b, e$}
	\Comment{Find $n$ in $T[b, b+1, \dots, e-1]$}
	\State \textbf{assert} $b < e$
	\If {$b + 1 = e$}
		\State \Return $b$
	\Else
		\State $m \gets \floor{(b+e)/2}$
		\If {$T[m] > n$}
			\State \Return $\mathrm{FindPos}(n, T, b, m)$
		\Else
			\State \Return $\mathrm{FindPos}(n, T, m+1, e)$
		\EndIf
	\EndIf
\EndFunction
	\\
\Function{Sort}{$T$}
	\State $n \gets \mathrm{size}(T)$
	\State $S \gets [ T[0] ]$
	\For{$i = 1$ \textbf{to} $n-1$}
		\State $p \gets \mathrm{FindPos}(T[i], S, 0, \mathrm{size}(S))$
		\State \textbf{insert} $T[i]$ \textbf{in} $S$ \textbf{at} $p$
	\EndFor
	\State \Return $S$
\EndFunction
\end{algorithmic}
\caption{Binary insertion sort algorithm}
\end{algorithm}

@@

This sequence is linked to the construction of complete binary trees : $u_n$ is the sum of the depths of all nodes in the complete binary tree containing $n-1$ nodes (see \cite{btree}).

@@

$n=2$ : $C_2(e_1) = (1,2)^{e_1}$

$n=3$ : $C_3(e_1,e_2,e_3) = (1,2)^{e_1} \circ (2,3)^{e_2} \circ (1,2)^{e_3}$

$n=4$ : $C_4(e_1,e_2,e_3,e_4,e_5) = (1, 2)^{e_1} \circ (3,4)^{e_2} \circ
(1,3)^{e_3} \circ (2, 4)^{e_4} \circ (1,2)^{e_5}$

@@

$$C_2 = (1,2)$$

$$C_3 = (1,2)(2,3)(1,2)$$

$$C_4 = (1,2)(3,4)(1,3)(2,4)(1,2)$$

@@

$$C_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$

@@

$$
\begin{aligned}
    C_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
        & = & (0,1)(2,3)(4,5)(6,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,4)(1,5)(2,6)(3,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,1)(2,3)(4,5)(6,7)
\end{aligned}$$

@@

For $n$ which is not a power of two, we construct $C_n^0$ by taking
$C_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.

For example, $C_5^0$ can be generated from $C_8^0$ and by removing quite a lot
of the boxes. We obtain the following solution :

$$C_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$

@@

\begin{thebibliography}{1}

\bibitem{btree}Sung-Hyuk Cha, {\em On Integer Sequences Derived from Balanced k-ary Trees}, Applied Mathematics in Electrical and Computer Engineering, 2012.

\end{thebibliography}
